---
title: "Exploratory Analysis"
author: "Venukanan Subenthiran"
date: '2022-11-12'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("R_Studio_Global_Variables.RData")
```

# Explorartoy Analysis

## Sub-setting the Data

```{r}

fraudTotal.db_fraud <- subset(fraudTotal.db, is_fraud == 1)
nrow(fraudTotal.db_fraud)

```
## Does Having a Higher City Population Have More Fraud?
```{r}
#install.packages("ggplot2")

fraudTotal.db_fraud$city_pop <- ifelse(fraudTotal.db_fraud$city_pop < mean(fraudTotal.db_fraud$city_pop), 0, 1)

library(ggplot2)

fraud_based_on_city_pop <- ggplot(data = fraudTotal.db_fraud, aes(x = factor(city_pop), fill = city_pop)) + geom_bar(stat = "count", width = 0.7, alpha = 0.7) + ggtitle("Fraudulent Transactions By City Population") + xlab("City Population Above or Below Average") + ylab("Number of Fraudulent Transactions") + scale_x_discrete(labels = c("Below City Population Average", "Above City Population Average")) + theme(legend.position = "none")
fraud_based_on_city_pop


```

### What type merchants receive more fraudulant transactions?
```{r}

category_table <- table(fraudTotal.db_fraud$category)
category_table
category_fraud.db <- as.data.frame(category_table)
colnames(category_fraud.db)[1] <- "Category Type"

#install.packages("treemap")
library(treemap)
treemap(category_fraud.db, index = "Category Type", vSize = "Freq", type = "index", title = "Merchant Category Types in Fraudulent Transactions", palette = "HCL", border.col = c("black"), border.lwds = 1, fontsize.labels = 10, fontcolor.labels = "white", fontface.labels = 1, bg.labels = c(0), align.labels = c("left", "top"), overlap.labels = 0.5, inflate.labels = T)

```

### Are fraud transactions commited more by males of females?
```{r}

gender_table <- table(fraudTotal.db_fraud$gender)
gender_fraud.db <- as.data.frame(gender_table)
colnames(gender_fraud.db)[1] <- "Gender"



library(ggplot2)

fraud_based_on_gender <- ggplot(data = gender_fraud.db, aes(x = Gender, y = Freq , fill = Gender)) + geom_bar(stat = "identity", width = 0.7, alpha = 0.7) + ggtitle("Fraudulent Transactions By Gender") + xlab("Fradulent Transactions Committed Based on Gender") + ylab("Number of Fraudulent Transactions") + scale_x_discrete(labels = c("Fradulent Transactions Committed by Female", "Fradulent Transactions Committed by Male")) + theme(legend.position = "none")
fraud_based_on_gender

```

## Normalization of Numeric Values

## Change Gender to numeric
```{r}
fraudTotal.db$gender <- ifelse(fraudTotal.db$gender == "M", 1, 0)

```

### Applying normalization to numeric variables

```{r}

data2 <- fraudTotal.db[c(3, 6, 9, 13, 14, 15, 16, 20, 21, 22, 23)]
#, 9
summary(data2)
#install.packages("caret")
library(caret)

fraudTotal.db_process <- preProcess(as.data.frame(data2), method = c("range"))

fraudTotal.db_norm <- predict(fraudTotal.db_process, as.data.frame(data2))
```

### Merging the fraudTotal.db and fraud.db_norm.
```{r}

fraudTotal.db$cc_num <- fraudTotal.db_norm$cc_num
fraudTotal.db$amt <- fraudTotal.db_norm$amt
fraudTotal.db$gender <- fraudTotal.db_norm$gender
fraudTotal.db$zip <- fraudTotal.db_norm$zip
fraudTotal.db$lat <- fraudTotal.db_norm$lat
fraudTotal.db$long <- fraudTotal.db_norm$long
fraudTotal.db$city_pop <- fraudTotal.db_norm$city_pop
fraudTotal.db$unix_time <- fraudTotal.db_norm$unix_time
fraudTotal.db$merch_lat <- fraudTotal.db_norm$merch_lat
fraudTotal.db$merch_long <- fraudTotal.db_norm$merch_long
fraudTotal.db$is_fraud <- fraudTotal.db_norm$is_fraud

```