---
title: "Demensionality Reduction"
author: "Venukanan Subenthiran"
date: "2022-11-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load("R_Studio_Global_Variables.RData")
```


# Feature Selection Using Forward Selection for Numeric Variables
```{r}
#install.packages("olsrr")
library(olsrr)

lm_model_numeric <- lm(is_fraud~trans_date_trans_time+cc_num+amt+zip+lat+long+city_pop+dob+unix_time+merch_lat+merch_long, data = fraudTotal.db)

FWD_fit_num <- ols_step_forward_p(lm_model_numeric, penter=0.05)

FWD_fit_num

```

#Converting all Categorical variables to numeric.
```{r}

fraudTotal.db_fact_num <- fraudTotal.db

str(fraudTotal.db_fact_num)
fraudTotal.db_fact_num$trans_date_trans_time <- as.numeric(fraudTotal.db_fact_num$trans_date_trans_time)
fraudTotal.db_fact_num$merchant <- as.numeric(fraudTotal.db_fact_num$merchant)
fraudTotal.db_fact_num$category <- as.numeric(fraudTotal.db_fact_num$category)
fraudTotal.db_fact_num$first <- as.numeric(fraudTotal.db_fact_num$first)
fraudTotal.db_fact_num$last <- as.numeric(fraudTotal.db_fact_num$last)
fraudTotal.db_fact_num$gender <- as.numeric(fraudTotal.db_fact_num$gender)
fraudTotal.db_fact_num$street <- as.numeric(fraudTotal.db_fact_num$street)
fraudTotal.db_fact_num$city <- as.numeric(fraudTotal.db_fact_num$city)
fraudTotal.db_fact_num$state <- as.numeric(fraudTotal.db_fact_num$state)
fraudTotal.db_fact_num$job <- as.numeric(fraudTotal.db_fact_num$job)
fraudTotal.db_fact_num$dob <- as.numeric(fraudTotal.db_fact_num$dob)
fraudTotal.db_fact_num$trans_num <- as.numeric(fraudTotal.db_fact_num$trans_num)


```


# Feature Selection Using Forward Selection for Categorical Variables
```{r}

lm_model_cat <- lm(is_fraud~merchant + category + first + last + gender + street + city + state + job + trans_num, data = fraudTotal.db_fact_num)

FWD_fit_cat <- ols_step_forward_p(lm_model_cat, penter=0.05)

FWD_fit_cat

```


```


### Chi Square test of merchant and category
```{r}

chisq.test(fraudTotal.db$merchant, fraudTotal.db$category)

# Category variable to be removed

```
### Chi Square test of first and last
```{r}

chisq.test(fraudTotal.db$first, fraudTotal.db$last)

# Last variable to be removed

```
### Chi Square test of first and gender
```{r}

chisq.test(fraudTotal.db$first, fraudTotal.db$gender)

```
### Chi Square test of street and city
```{r}

chisq.test(fraudTotal.db$street, fraudTotal.db$city)

```

### Chi Square test of city and state
```{r}

chisq.test(fraudTotal.db$city, fraudTotal.db$state)

```


### Chi Square test of category and job
```{r}

chisq.test(fraudTotal.db$category, fraudTotal.db$job)

```

### Chi Square test of gender and job
```{r}

chisq.test(fraudTotal.db$gender, fraudTotal.db$job)

```

### Chi Square test of category and trans_num
```{r}

chisq.test(fraudTotal.db$category, fraudTotal.db$trans_num)

```
