---
title: "Bivariate Analysis"
author: "Venukanan Subenthiran"
date: "2022-11-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Bivariate Analysis of fraudTotal.db data frame

```{r}
sum(is.na(fraudTotal.db))
```

```{r}
str(fraudTotal.db)
```



## The correlation between numeric attributes
```{r}
#install.packages("corrplot")
library(corrplot)

subset_fraudTotal.db <- subset(fraudTotal.db, select = c(3, 6, 13, 14, 15, 16, 20, 21, 22, 23))
corrplot(cor(subset_fraudTotal.db), method = "number")


```

## Correlation Analysis of Numeric Variables

### Correlation of zip, lat, long, merch_lat, and merch_long
```{r}

cor.test(fraudTotal.db$zip, fraudTotal.db$lat, method = "pearson")

cor.test(fraudTotal.db$zip, fraudTotal.db$long, method = "pearson")

cor.test(fraudTotal.db$zip, fraudTotal.db$merch_lat, method = "pearson")

cor.test(fraudTotal.db$zip, fraudTotal.db$merch_long, method = "pearson")

```
### Correlation of is_fraud and amt
```{r}

cor.test(fraudTotal.db$is_fraud, fraudTotal.db$amt, method = "pearson")

```
### Correlation of is_fraud and city_pop
```{r}

cor.test(fraudTotal.db$is_fraud, fraudTotal.db$city_pop, method = "pearson")

```





### Scatterplot of zip and long

```{r}
plot(fraudTotal.db$zip, fraudTotal.db$long, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Zip Code", ylab = "Longitude")
```

## Scatterplot of amt and is_fraud

```{r}
plot(fraudTotal.db$amt, fraudTotal.db$is_fraud, main = "Scatterplot of amount and Is Fraud", xlab = "Amount", ylab = "Is Fraud")
```

## Scatterplot of Amt and city_pop

```{r}
plot(fraudTotal.db$city_pop, fraudTotal.db$amt, main = "Scatterplot of City Population vs Amount", xlab = "City Population", ylab = "Amount")
```

## Scatterplot of lat and is_fraud

```{r}
#plot(fraudTotal.db$lat, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```

## Scatterplot of long and is_fraud

```{r}
#plot(fraudTotal.db$long, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```

## Scatterplot of city_pop and is_fraud

```{r}
plot(fraudTotal.db$city_pop, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```

## Scatterplot of unix_time and is_fraud

```{r}
#plot(fraudTotal.db$unix_time, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```

## Scatterplot of merch_lat and is_fraud

```{r}
#plot(fraudTotal.db$merch_lat, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```

## Scatterplot of merch_long and is_fraud

```{r}
#plot(fraudTotal.db$merch_long, fraudTotal.db$is_fraud, main = "Scatterplot of credit card Number and Is Fraud", xlab = "Transaction Date and Time", ylab = "Is Fraud")
```








## Correlation of Categorical Variables

### Chi Square test of merchant and category
```{r}

chisq.test(fraudTotal.db$merchant, fraudTotal.db$category)

```
### Chi Square test of first and last
```{r}

chisq.test(fraudTotal.db$first, fraudTotal.db$last)

```
### Chi Square test of first and gender
```{r}

chisq.test(fraudTotal.db$first, fraudTotal.db$gender)

```
### Chi Square test of street and city
```{r}

chisq.test(fraudTotal.db$street, fraudTotal.db$city)

```

### Chi Square test of city and state
```{r}

chisq.test(fraudTotal.db$city, fraudTotal.db$state)

```


### Chi Square test of category and job
```{r}

chisq.test(fraudTotal.db$category, fraudTotal.db$job)

```

### Chi Square test of gender and job
```{r}

chisq.test(fraudTotal.db$gender, fraudTotal.db$job)

```

### Chi Square test of category and trans_num
```{r}

chisq.test(fraudTotal.db$category, fraudTotal.db$trans_num)

```