---
title: "Univariate Analysis"
author: "Venukanan Subenthiran"
date: "2022-11-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#load("R_Studio_Global_Variables.RData")
```


# Understanding the Datafram as a Whole
## Provides baseline for creating a more details data dictionary.
```{r}

str(fraudTotal.db)

```



## Unvirariate Analysis of trans_date_trans_time 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_date_trans_time)) 
```

### Converting Character to DateTime class

```{r}
#install.packages("lubridate")
library(lubridate)

fraudTotal.db$trans_date_trans_time <- ymd_hms(fraudTotal.db$trans_date_trans_time)
```

### Summary of trans_date_trans_time column

```{r}
summary(fraudTotal.db$trans_date_trans_time)
```

### Histogram of trans_date_trans_time variable

```{r}
hist(fraudTotal.db$trans_date_trans_time, breaks = 10 , main = "Histogram of Date/Time Data Collected", xlab = "trans_date_trans_time in Years")
```

## Univariate Analysis of cc_num 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$cc_num)) 
```

### Summary of cc_num column

```{r}
options(scipen = 999)
summary(fraudTotal.db$cc_num)
```

### Find the Standard Deviation and Variance of cc_num variable

```{r}
sd(fraudTotal.db$cc_num)
var(fraudTotal.db$cc_num)
```


### Frequency of cc_num values

```{r}
table_cc_num <- table(fraudTotal.db$cc_num)
head(table_cc_num)
```

### Unique Values of cc_num
```{r}
head(unique(fraudTotal.db$cc_num))
```



### Histogram of cc_num

```{r}
hist(fraudTotal.db$cc_num, main = "Historgram of Credit Card Numbers", xlab = "Credit Card Numbers")

```
### Boxplot of cc_num variable
```{r}
boxplot(fraudTotal.db$cc_num)
```

## Univariate Analysis of merchant

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merchant)) 
```
### Summary of merchant column

```{r}
summary(fraudTotal.db$merchant)
```
### Check to see all Unique Values
```{r}

head(unique(fraudTotal.db$merchant))

```
```{r}
table_merchant <- table(fraudTotal.db$merchant)
head(table_merchant)
```




### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$merchant <- as.factor(fraudTotal.db$merchant)
class(fraudTotal.db$merchant)

```

### Frequency Distribution of trans_date_trans_time variable

```{r}
barplot(table(fraudTotal.db$merchant), main = "Frequency Distribution of Merchants", xlab = "Merchants", ylab = "Frequency")
```

## Univariate Analysis of category 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$category)) 
```

### Summary of category Column

```{r}
summary(fraudTotal.db$category)
class(fraudTotal.db$category)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

### Frequency of category values

```{r}
table(fraudTotal.db$category)
```

## Frequency Distribution of category

```{r}
barplot(table(fraudTotal.db$category), las = 3, main = "Frequency Distribution of Merchant Categories", xlab = "", ylab = "Frequency") 
mtext("Catgory Values", side = 1)

```


## Univariate Analysis of amt 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$amt)) 
```

### Summary of amt Column

```{r}
summary(fraudTotal.db$amt)
class(fraudTotal.db$amt)
```

### Find the Standard Deviation and Variance of amt Column

```{r}
sd(fraudTotal.db$amt)
var(fraudTotal.db$amt)
```

### Frequency of amt Column

```{r}
table_amt <- table(fraudTotal.db$amt)
head(table_amt)
```

### Frequency Distribution of amt Column

```{r}
barplot(table(fraudTotal.db$amt), las = 3, main = "Frequency Distribution of Amount", xlab = "", ylab = "Frequency") 
mtext("Amount Values", side = 1)

```
## Boxplot of amt Column

```{r}

boxplot(fraudTotal.db$amt)

# does not look good.
# displying the number of outliers existing with the data??

```

## Univariate Analysis of first 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$first)) 
```

### Summary of first Column

```{r}
summary(fraudTotal.db$first)
class(fraudTotal.db$first)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$first <- as.factor(fraudTotal.db$first)
```


### Frequency of first
```{r}
table_first <- table(fraudTotal.db$first)
head(table_first)
```

### Frequency Distribution of first

```{r}
barplot(table(fraudTotal.db$first), las = 3, main = "Frequency Distribution of first Field", xlab = "", ylab = "Frequency") 
mtext("First Names of Card Holders", side = 1)

```

## Univariate Analysis of last 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$last)) 
```

### Summary of last Column

```{r}
summary(fraudTotal.db$last)
class(fraudTotal.db$last)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$last <- as.factor(fraudTotal.db$last)
```


### Frequency of last

```{r}
table_last <- table(fraudTotal.db$last)
head(table_last)
```

### Frequency Distribution of last

```{r}
barplot(table(fraudTotal.db$last), las = 3, main = "Frequency Distribution of last Field", xlab = "", ylab = "Frequency") 
mtext("Last Names of Card Holders", side = 1)

```


## Univariate Analysis of gender 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$gender)) 
```

### Summary of gender Column

```{r}
summary(fraudTotal.db$gender)
class(fraudTotal.db$gender)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$gender <- as.factor(fraudTotal.db$gender)
```


### Frequency of gender

```{r}
table(fraudTotal.db$gender)
```

## Frequency Distribution of gender

```{r}
barplot(table(fraudTotal.db$gender), las = 1, main = "Frequency Distribution of Gender", xlab = "", ylab = "Frequency") 
mtext("Gender", side = 1)

```

## Univariate Analysis of street 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$street)) 
```

### Summary of street Column

```{r}
summary(fraudTotal.db$street)
class(fraudTotal.db$street)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$street <- as.factor(fraudTotal.db$street)
```


### Frequency of Street

```{r}
table_street <- table(fraudTotal.db$street)
head(table_street)
```

### Frequency Distribution of street

```{r}
barplot(table(fraudTotal.db$street), las = 3, main = "Frequency Distribution of Addresses", xlab = "", ylab = "Frequency") 
mtext("Addresses", side = 1)

```

## Univariate Analysis of city 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$city)) 
```

### Summary of city Column

```{r}
summary(fraudTotal.db$city)
class(fraudTotal.db$city)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$city <- as.factor(fraudTotal.db$city)
```


### Frequency of city

```{r}
table_city <- table(fraudTotal.db$city)
head(table_city)
```

### Frequency Distribution of city

```{r}
barplot(table(fraudTotal.db$city), las = 3, main = "Frequency Distribution of Cities", xlab = "", ylab = "Frequency") 
mtext("Cities", side = 1)

```



## Univariate Analysis of state 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$state)) 
```

### Summary of state Column

```{r}
summary(fraudTotal.db$state)
class(fraudTotal.db$state)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$state <- as.factor(fraudTotal.db$state)
```


### Frequency of state

```{r}
table(fraudTotal.db$state)
```

### Frequency Distribution of state

```{r}
barplot(table(fraudTotal.db$state), las = 3, main = "Frequency Distribution of States", xlab = "", ylab = "Frequency") 
mtext("States", side = 1)

```

## Univariate Analysis of zip 

###Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$zip)) 
```

### Summary of zip Column

```{r}
summary(fraudTotal.db$zip)
class(fraudTotal.db$zip)
```


### Find the Standard Deviation and Variance of zip variable

```{r}
sd(fraudTotal.db$zip)
var(fraudTotal.db$zip)
```

### Frequency of zip

```{r}
table_zip <- table(fraudTotal.db$zip)
head(table_zip)
```

### Frequency Distribution of zip

```{r}
barplot(table(fraudTotal.db$zip), las = 3, main = "Frequency Distribution of Zip Codes", xlab = "", ylab = "Frequency") 
mtext("Zip Codes", side = 1)

```

## Univariate Analysis of lat 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$lat)) 
```

### Summary of lat Column

```{r}
summary(fraudTotal.db$lat)
class(fraudTotal.db$lat)
```


### Find the Standard Deviation and Variance of lat variable

```{r}
sd(fraudTotal.db$lat)
var(fraudTotal.db$lat)
```

### Frequency of lat

```{r}
table_lat <- table(fraudTotal.db$lat)
head(table_lat)
```

### Frequency Distribution of lat

```{r}
barplot(table(fraudTotal.db$lat), las = 3, main = "Frequency Distribution of Latitude", xlab = "", ylab = "Frequency") 
mtext("Latitude", side = 1)

```

## Univariate Analysis of long 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$long)) 
```

### Summary of long Column

```{r}
summary(fraudTotal.db$long)
class(fraudTotal.db$long)
```


### Find the Standard Deviation and Variance of long variable

```{r}
sd(fraudTotal.db$long)
var(fraudTotal.db$long)
```

### Frequency of long

```{r}
table_long <- table(fraudTotal.db$long)
head(table_long)
```

### Frequency Distribution of long

```{r}
barplot(table(fraudTotal.db$long), las = 3, main = "Frequency Distribution of Longitude", xlab = "", ylab = "Frequency") 
mtext("Longitude", side = 1)

```

## Univariate Analysis of city_pop 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$city_pop)) 
```

### Summary of city_pop Column

```{r}
summary(fraudTotal.db$city_pop)
class(fraudTotal.db$city_pop)
```


### Find the Standard Deviation and Variance of city_pop variable

```{r}
sd(fraudTotal.db$city_pop)
var(fraudTotal.db$city_pop)
```

### Frequency of city_pop

```{r}
table_city_pop <- table(fraudTotal.db$city_pop)
head(table_city_pop)
```

### Frequency Distribution of city_pop

```{r}
barplot(table(fraudTotal.db$city_pop), las = 3, main = "Frequency Distribution of City Population", xlab = "", ylab = "Frequency") 
mtext("City Population", side = 1)

```

## Univariate Analysis of job 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$job)) 
```

### Summary of job Column

```{r}
summary(fraudTotal.db$job)
class(fraudTotal.db$job)
```

### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$job <- as.factor(fraudTotal.db$job)
```


### Frequency of job

```{r}
table_job <- table(fraudTotal.db$job)
head(table_job)
```

### Frequency Distribution of job

```{r}
barplot(table(fraudTotal.db$job), las = 3, main = "Frequency Distribution of Jobs", xlab = "", ylab = "Frequency") 
mtext("Jobs of Card Holders", side = 1)

```

## Univariate Analysis of dob 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$dob)) 
```
### Converting Character to DateTime class

```{r}
library(lubridate)

fraudTotal.db$dob <- ymd(fraudTotal.db$dob)
```

### Summary of dob Column

```{r}
summary(fraudTotal.db$dob)
class(fraudTotal.db$dob)
```


### Find the Standard Deviation and Variance of dob variable

```{r}
sd(fraudTotal.db$dob)
var(fraudTotal.db$dob)
```

### Frequency of dob

```{r}
table_dob <- table(fraudTotal.db$dob)
head(table_dob)
```

### Frequency Distribution of dob

```{r}
barplot(table(fraudTotal.db$dob), las = 3, main = "Frequency Distribution of Date of Birth", xlab = "", ylab = "Frequency") 
mtext("Date of Birth of Card Holders", side = 1)

```

## Univariate Analysis of trans_num 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_num)) 
```

### Summary of trans_num Column

```{r}
summary(fraudTotal.db$trans_num)
class(fraudTotal.db$trans_num)
```
### Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$trans_num <- as.factor(fraudTotal.db$trans_num)
```


### Frequency of trans_num

```{r}
table_trans_num <- table(fraudTotal.db$trans_num)
head(table_trans_num)
```

### Frequency Distribution of trans_num

```{r}
barplot(table(fraudTotal.db$trans_num), las = 3, main = "Frequency Distribution of Transation Number", xlab = "", ylab = "Frequency") 
mtext("Transaction Numbers", side = 1)

```


## Univariate Analysis of unix_time 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$unix_time)) 
```

### Summary of unix_time Column

```{r}
summary(fraudTotal.db$unix_time)
class(fraudTotal.db$unix_time)
```


### Find the Standard Deviation and Variance of unix_time variable

```{r}
sd(fraudTotal.db$unix_time)
var(fraudTotal.db$unix_time)
```

### Frequency of unix_time

```{r}
table_unix_time <- table(fraudTotal.db$unix_time)
head(table_unix_time)
```

### Frequency Distribution of unix_time

```{r}
barplot(table(fraudTotal.db$unix_time), las = 3, main = "Frequency Distribution of Unix Time", xlab = "", ylab = "Frequency") 
mtext("Unix Time", side = 1)

```

## Univariate Analysis of merch_long 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merch_long)) 
```

### Summary of merch_long Column

```{r}
summary(fraudTotal.db$merch_long)
class(fraudTotal.db$merch_long)
```


### Find the Standard Deviation and Variance of merch_long variable

```{r}
sd(fraudTotal.db$merch_long)
var(fraudTotal.db$merch_long)
```

### Frequency of merch_long

```{r}
table_merch_long <- table(fraudTotal.db$merch_long)
head(table_merch_long)
```

### Frequency Distribution of merch_long

```{r}
barplot(table(fraudTotal.db$merch_long), las = 3, main = "Frequency Distribution of Merchant Longitude", xlab = "", ylab = "Frequency")
mtext("Merchant Longitude", side = 1)
```

## Univariate Analysis of merch_lat 

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merch_lat)) 
```

### Summary of merch_lat Column

```{r}
summary(fraudTotal.db$merch_lat)
class(fraudTotal.db$merch_lat)
```

### Find the Standard Deviation and Variance of merch_lat variable

```{r}
sd(fraudTotal.db$merch_lat)
var(fraudTotal.db$merch_lat)
```

### Frequency of merch_lat

```{r}
table_merch_lat <- table(fraudTotal.db$merch_lat)
head(table_merch_lat)
```

### Frequency Distribution of lat

```{r}
barplot(table(fraudTotal.db$merch_lat), las = 3, main = "Frequency Distribution of Merchant Latitude", xlab = "", ylab = "Frequency") 
mtext("Merchant Longitude", side = 1)

```






## Univariate Analysis of is_fraud (Dependent Variable)

### Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$is_fraud)) 
```

### Summary of is_fraud Column

```{r}
summary(fraudTotal.db$is_fraud)
class(fraudTotal.db$is_fraud)
```


### Find the Standard Deviation and Variance of cc_num variable

```{r}
sd(fraudTotal.db$is_fraud)
var(fraudTotal.db$is_fraud)
```

### Frequency of is_fraud

```{r}
table(fraudTotal.db$is_fraud)
```

### Frequency Distribution of is_fraud

```{r}
barplot(table(fraudTotal.db$is_fraud), las = 3, main = "Frequency Distribution of Fradulant Transaction", xlab = "", ylab = "Frequency") 
mtext("Fraudulant Transactions", side = 1)

```



