---
title: "Univariate Analysis"
author: "Venukanan Subenthiran"
<<<<<<< HEAD
date: '2022-11-10'
=======
date: "2022-11-09"
>>>>>>> 771b459096335833e88d99e06476c521b0980a35
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
# Unvirariate Analysis of trans_date_trans_time 

## Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_date_trans_time)) 
```

## Converting Character to DateTime class

```{r}
library(lubridate)

fraudTotal.db$trans_date_trans_time <- ymd_hms(fraudTotal.db$trans_date_trans_time)
```

## Summary of trans_date_trans_time column

```{r}
summary(fraudTotal.db$trans_date_trans_time)
```

## Histogram of trans_date_trans_time variable

```{r}
hist(fraudTotal.db$trans_date_trans_time, breaks = 10, main = "Histogram of Date/Time Data Collected", xlab = "trans_date_trans_time in Years")
```

# Univariate Analysis of cc_num 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$cc_num)) 
```

## Summary of cc_num column

```{r}
options(scipen = 999)
summary(fraudTotal.db$cc_num)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
sd(fraudTotal.db$cc_num)
var(fraudTotal.db$cc_num)
```

## Frequency of cc_num

```{r}
table(fraudTotal.db$cc_num)
```

## Histogram of cc_num

```{r}
hist(fraudTotal.db$cc_num, main = "Historgram of cc_num", xlab = "cc_num Values")

```

```{r}
boxplot(fraudTotal.db$cc_num)
```

# Univariate Analysis of merchant

## Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merchant)) 
```
## Summary of merchant column

```{r}
summary(fraudTotal.db$merchant)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$merchant <- as.factor(fraudTotal.db$merchant)
class(fraudTotal.db$merchant)
```

## Frequency Distribution of trans_date_trans_time variable

```{r}
barplot(table(fraudTotal.db$merchant))

#hist(fraudTotal.db$merchant, breaks = 10, main = "Histogram of merchant", xlab = "trans_date_trans_time in Years")
```

# Univariate Analysis of category 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$category)) 
```

## Summary of category Column

```{r}
summary(fraudTotal.db$category)
class(fraudTotal.db$category)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of category

```{r}
table(fraudTotal.db$category)
```

## Frequency Distribution of category

```{r}
barplot(table(fraudTotal.db$category), las = 3, main = "Frequency Distribution of category Field", xlab = "") 
mtext("catgory Values", side = 1)

```


# Univariate Analysis of amt 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$amt)) 
```

## Summary of amt Column

```{r}
summary(fraudTotal.db$amt)
class(fraudTotal.db$amt)
```

## Find the Standard Deviation and Variance of amt Column

```{r}
sd(fraudTotal.db$amt)
var(fraudTotal.db$amt)
```

## Frequency of amt Column

```{r}
table(fraudTotal.db$amt)
```

## Frequency Distribution of amt Column

```{r}
barplot(table(fraudTotal.db$amt), las = 3, main = "Frequency Distribution of amt Field", xlab = "") 
mtext("amt Values", side = 1)

```
## Boxplot of amt Column

```{r}

boxplot(fraudTotal.db$amt)

# does not look good.
# displying the number of outliers existing with the data??

```

# Univariate Analysis of first 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$first)) 
```

## Summary of first Column

```{r}
summary(fraudTotal.db$first)
class(fraudTotal.db$first)
```
## Convert Characater Class to a Factor Class
```{r}
#fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of first

```{r}
table(fraudTotal.db$first)
```

## Frequency Distribution of first

```{r}
barplot(table(fraudTotal.db$first), las = 3, main = "Frequency Distribution of first Field", xlab = "") 
mtext("first Values", side = 1)

```

# Univariate Analysis of last 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$last)) 
```

## Summary of last Column

```{r}
summary(fraudTotal.db$last)
class(fraudTotal.db$last)
```
## Convert Characater Class to a Factor Class
```{r}
#fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of last

```{r}
table(fraudTotal.db$last)
```

## Frequency Distribution of last

```{r}
barplot(table(fraudTotal.db$last), las = 3, main = "Frequency Distribution of last Field", xlab = "") 
mtext("last Values", side = 1)

```


# Univariate Analysis of gender 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$gender)) 
```

## Summary of gender Column

```{r}
summary(fraudTotal.db$gender)
class(fraudTotal.db$gender)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$gender <- as.factor(fraudTotal.db$gender)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$gender)
#var(fraudTotal.db$category)
```

## Frequency of gender

```{r}
table(fraudTotal.db$gender)
```

## Frequency Distribution of gender

```{r}
barplot(table(fraudTotal.db$gender), las = 3, main = "Frequency Distribution of gender Field", xlab = "") 
mtext("gender Values", side = 1)

```

# Univariate Analysis of street 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$street)) 
```

## Summary of street Column

```{r}
summary(fraudTotal.db$street)
class(fraudTotal.db$street)
```
## Convert Characater Class to a Factor Class
```{r}
#fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of category

```{r}
table(fraudTotal.db$street)
```

## Frequency Distribution of category

```{r}
barplot(table(fraudTotal.db$street), las = 3, main = "Frequency Distribution of street Field", xlab = "") 
mtext("street Values", side = 1)

```

# Univariate Analysis of city 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$city)) 
```

## Summary of city Column

```{r}
summary(fraudTotal.db$city)
class(fraudTotal.db$city)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$city <- as.factor(fraudTotal.db$city)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of city

```{r}
table(fraudTotal.db$city)
```

## Frequency Distribution of city

```{r}
barplot(table(fraudTotal.db$city), las = 3, main = "Frequency Distribution of city Field", xlab = "") 
mtext("city Values", side = 1)

```



# Univariate Analysis of state 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$state)) 
```

## Summary of state Column

```{r}
summary(fraudTotal.db$state)
class(fraudTotal.db$state)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$state <- as.factor(fraudTotal.db$state)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of category

```{r}
table(fraudTotal.db$state)
```

## Frequency Distribution of category

```{r}
barplot(table(fraudTotal.db$state), las = 3, main = "Frequency Distribution of state Field", xlab = "") 
mtext("state Values", side = 1)

```

# Univariate Analysis of zip 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$zip)) 
```

## Summary of zip Column

```{r}
summary(fraudTotal.db$zip)
class(fraudTotal.db$zip)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$zip <- as.factor(fraudTotal.db$zip)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$zip)
#var(fraudTotal.db$category)
```

## Frequency of zip

```{r}
table(fraudTotal.db$zip)
```

## Frequency Distribution of zip

```{r}
barplot(table(fraudTotal.db$zip), las = 3, main = "Frequency Distribution of zip Field", xlab = "") 
mtext("zip Values", side = 1)

```

# Univariate Analysis of lat 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$lat)) 
```

## Summary of lat Column

```{r}
summary(fraudTotal.db$lat)
class(fraudTotal.db$lat)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$lat <- as.factor(fraudTotal.db$lat)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of lat

```{r}
table(fraudTotal.db$lat)
```

## Frequency Distribution of lat

```{r}
barplot(table(fraudTotal.db$lat), las = 3, main = "Frequency Distribution of lat Field", xlab = "") 
mtext("lat Values", side = 1)

```

# Univariate Analysis of long 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$long)) 
```

## Summary of long Column

```{r}
summary(fraudTotal.db$long)
class(fraudTotal.db$long)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$long <- as.factor(fraudTotal.db$long)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of long

```{r}
table(fraudTotal.db$long)
```

## Frequency Distribution of long

```{r}
barplot(table(fraudTotal.db$long), las = 3, main = "Frequency Distribution of long Field", xlab = "") 
mtext("long Values", side = 1)

```

# Univariate Analysis of city_pop 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$city_pop)) 
```

## Summary of city_pop Column

```{r}
summary(fraudTotal.db$city_pop)
class(fraudTotal.db$city_pop)
```
## Convert Characater Class to a Factor Class
```{r}
#fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of city_pop variable

```{r}
sd(fraudTotal.db$city_pop)
var(fraudTotal.db$city_pop)
```

## Frequency of city_pop

```{r}
table(fraudTotal.db$city_pop)
```

## Frequency Distribution of city_pop

```{r}
barplot(table(fraudTotal.db$city_pop), las = 3, main = "Frequency Distribution of city_pop Field", xlab = "") 
mtext("city_pop Values", side = 1)

```

# Univariate Analysis of job 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$job)) 
```

## Summary of job Column

```{r}
summary(fraudTotal.db$job)
class(fraudTotal.db$job)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$job <- as.factor(fraudTotal.db$job)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of job

```{r}
table(fraudTotal.db$job)
```

## Frequency Distribution of job

```{r}
barplot(table(fraudTotal.db$job), las = 3, main = "Frequency Distribution of job Field", xlab = "") 
mtext("job Values", side = 1)

```

# Univariate Analysis of dob 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$dob)) 
```
## Converting Character to DateTime class

```{r}
library(lubridate)

fraudTotal.db$dob <- ymd(fraudTotal.db$dob)
```

## Summary of dob Column

```{r}
summary(fraudTotal.db$dob)
class(fraudTotal.db$dob)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of dob variable

```{r}
sd(fraudTotal.db$dob)
var(fraudTotal.db$dob)
```

## Frequency of dob

```{r}
table(fraudTotal.db$dob)
```

## Frequency Distribution of dob

```{r}
barplot(table(fraudTotal.db$dob), las = 3, main = "Frequency Distribution of dob Field", xlab = "") 
mtext("dob Values", side = 1)

```

# Univariate Analysis of job 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_num)) 
```

## Summary of job Column

```{r}
summary(fraudTotal.db$trans_num)
class(fraudTotal.db$trans_num)
```
## Convert Characater Class to a Factor Class
```{r}
#fraudTotal.db$trans_num <- as.factor(fraudTotal.db$trans_num)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of trans_num

```{r}
table(fraudTotal.db$trans_num)
```

## Frequency Distribution of trans_num

```{r}
barplot(table(fraudTotal.db$trans_num), las = 3, main = "Frequency Distribution of trans_num Field", xlab = "") 
mtext("trans_num Values", side = 1)

```


# Univariate Analysis of unix_time 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$unix_time)) 
```

## Summary of unix_time Column

```{r}
summary(fraudTotal.db$unix_time)
class(fraudTotal.db$unix_time)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$job <- as.factor(fraudTotal.db$job)
```

## Find the Standard Deviation and Variance of unix_time variable

```{r}
sd(fraudTotal.db$unix_time)
var(fraudTotal.db$unix_time)
```

## Frequency of unix_time

```{r}
table(fraudTotal.db$unix_time)
```

## Frequency Distribution of unix_time

```{r}
barplot(table(fraudTotal.db$unix_time), las = 3, main = "Frequency Distribution of unix_time Field", xlab = "") 
mtext("unix_time Values", side = 1)

```

# Univariate Analysis of merch_long 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merch_long)) 
```

## Summary of merch_long Column

```{r}
summary(fraudTotal.db$merch_long)
class(fraudTotal.db$merch_long)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$merch_long <- as.factor(fraudTotal.db$merch_long)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of merch_long

```{r}
table(fraudTotal.db$merch_long)
```

## Frequency Distribution of merch_long

```{r}
barplot(table(fraudTotal.db$merch_long), las = 3, main = "Frequency Distribution of merch_long Field", xlab = "") 
mtext("merch_long Values", side = 1)

```

# Univariate Analysis of merch_lat 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merch_lat)) 
```

## Summary of merch_lat Column

```{r}
summary(fraudTotal.db$merch_lat)
class(fraudTotal.db$merch_lat)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$merch_lat <- as.factor(fraudTotal.db$merch_lat)
```

## Find the Standard Deviation and Variance of merch_lat variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of merch_lat

```{r}
table(fraudTotal.db$merch_lat)
```

## Frequency Distribution of lat

```{r}
barplot(table(fraudTotal.db$merch_lat), las = 3, main = "Frequency Distribution of merch_lat Field", xlab = "") 
mtext("merch_lat Values", side = 1)

```

# Univariate Analysis of is_fraud 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$is_fraud)) 
```

## Summary of is_fraud Column

```{r}
summary(fraudTotal.db$is_fraud)
class(fraudTotal.db$is_fraud)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$is_fraud <- as.factor(fraudTotal.db$is_fraud)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of is_fraud

```{r}
table(fraudTotal.db$is_fraud)
```

## Frequency Distribution of is_fraud

```{r}
barplot(table(fraudTotal.db$is_fraud), las = 3, main = "Frequency Distribution of is_fraud Field", xlab = "") 
mtext("is_fraud Values", side = 1)

```


>>>>>>> 771b459096335833e88d99e06476c521b0980a35
