---
title: "Univariate Analysis"
author: "Venukanan Subenthiran"
date: '2022-11-10'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#trans_date_trans_time Unvirariate Analysis

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_date_trans_time)) 
```

## Converting Character to DateTime class

```{r}
library(lubridate)

fraudTotal.db$trans_date_trans_time <- ymd_hms(fraudTotal.db$trans_date_trans_time)
```

## Summary of trans_date_trans_time column

```{r}
summary(fraudTotal.db$trans_date_trans_time)
```

## Histogram of trans_date_trans_time variable

```{r}
hist(fraudTotal.db$trans_date_trans_time, breaks = 10, main = "Histogram of Date/Time Collected", xlab = "trans_date_trans_time in Years")
```

#cc_num Univariate Analysis

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$cc_num)) 
```

## Summary of cc_num column

```{r}
options(scipen = 999)
summary(fraudTotal.db$cc_num)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
sd(fraudTotal.db$cc_num)
var(fraudTotal.db$cc_num)
```

## Frequency of cc_num

```{r}
table(fraudTotal.db$cc_num)
```

## Histogram of cc_num

```{r}
hist(fraudTotal.db$cc_num, main = "Historgram of cc_num", xlab = "cc_num Values")

```

```{r}
boxplot(fraudTotal.db$cc_num)
```
