---
title: "Univariate Analysis"
author: "Venukanan Subenthiran"
<<<<<<< HEAD
date: '2022-11-10'
=======
date: "2022-11-09"
>>>>>>> 771b459096335833e88d99e06476c521b0980a35
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<<<<<<< HEAD
# Unvirariate Analysis of trans_date_trans_time 

## Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$trans_date_trans_time)) 
```

## Converting Character to DateTime class

```{r}
library(lubridate)

fraudTotal.db$trans_date_trans_time <- ymd_hms(fraudTotal.db$trans_date_trans_time)
```

## Summary of trans_date_trans_time column

```{r}
summary(fraudTotal.db$trans_date_trans_time)
```

## Histogram of trans_date_trans_time variable

```{r}
hist(fraudTotal.db$trans_date_trans_time, breaks = 10, main = "Histogram of Date/Time Data Collected", xlab = "trans_date_trans_time in Years")
```

# Univariate Analysis of cc_num 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$cc_num)) 
```

## Summary of cc_num column

```{r}
options(scipen = 999)
summary(fraudTotal.db$cc_num)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
sd(fraudTotal.db$cc_num)
var(fraudTotal.db$cc_num)
```

## Frequency of cc_num

```{r}
table(fraudTotal.db$cc_num)
```

## Histogram of cc_num

```{r}
hist(fraudTotal.db$cc_num, main = "Historgram of cc_num", xlab = "cc_num Values")

```

```{r}
boxplot(fraudTotal.db$cc_num)
```

# Univariate Analysis of merchant

## Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$merchant)) 
```
## Summary of merchant column

```{r}
summary(fraudTotal.db$merchant)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$merchant <- as.factor(fraudTotal.db$merchant)
class(fraudTotal.db$merchant)
```

## Frequency Distribution of trans_date_trans_time variable

```{r}
barplot(table(fraudTotal.db$merchant))

#hist(fraudTotal.db$merchant, breaks = 10, main = "Histogram of merchant", xlab = "trans_date_trans_time in Years")
```

# Univariate Analysis of category 

##Checking to see if any NA values exist

```{r}
sum(is.na(fraudTotal.db$category)) 
```

## Summary of category Column

```{r}
summary(fraudTotal.db$category)
class(fraudTotal.db$category)
```
## Convert Characater Class to a Factor Class
```{r}
fraudTotal.db$category <- as.factor(fraudTotal.db$category)
```

## Find the Standard Deviation and Variance of cc_num variable

```{r}
#sd(fraudTotal.db$category)
#var(fraudTotal.db$category)
```

## Frequency of category

```{r}
table(fraudTotal.db$category)
```

## Frequency Distribution of category

```{r}
barplot(table(fraudTotal.db$category), las = 3, main = "Frequency Distribution of category Field", xlab = "") 
mtext("catgory Values", side = 1)

```




```{r}

```



>>>>>>> 771b459096335833e88d99e06476c521b0980a35
